---
title: "lubridate"
subtitle: "Даты без боли"
author: | 
  | Калакуцкий Аркадий
  | Младший технический аналитик
  | JetBrains
date: "November 26, 2016"
output: 
  beamer_presentation:
    pandoc_args: [
      "--latex-engine=xelatex",
      "--include-in-header=fontoptions.tex"
    ]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## lubridate
это библиотека :)
```{r, include=TRUE, echo=TRUE}
library(lubridate)
```

## О моей задаче
О моей задаче

## О моей задаче
пример данных

## Как

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

